On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 bqp.tex
Make editorial changes and add more TODOs

\begin{thm}
	\protoref{BlindBQP} is IND-CPA
\end{thm}
\begin{proof}
	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\begin{thm}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item classical inputs
		\item client uses only X/Z measurements
		\item negl. completeness and soundness
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negl. completeness and soundness \Ethan{same inputs...?}
\end{thm}

\begin{rmk}
	The same construction works for $\FBQP$ too.
	\Ethan{Maybe say more? Where should I define $\FBQP$?}
\end{rmk}

>>>>

\begin{thm}
	\protoref{BlindBQP} is IND-CPA secure.
\end{thm}
\begin{proof}
	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\begin{thm}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item client's inputs are classical
		\item client doesn't applies any quantum gates, and uses only $X$ and $Z$ measurements
		\item completeness and soundness parameters are both negligible
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negligible completeness and soundness.
\end{thm}

\begin{rmk}
	The same construction works for $\FBQP$ too.
	\Ethan{Need to say more about amplification and doing this bit-by-bit. Also, where should I define $\FBQP$?}
\end{rmk}
